### 2010-06-16 docs/FAQ/faq.tex
typo
start a question on multigrid non-convergence

@@

\item {\em In the final projection in the algorithm, we project
  $U^{n+1}$, using a time-centered $\beta_0$, a time-centered $\rho_0$, but
  an ``$n+1$''-centered $S$.  When then is the resulting $\phi$ (which then
  defines $\pi$) is at ``$n+1/2$''?}

>>>>

\item {\em  MAESTRO crashes because the multigrid algorithm fails to
    converge---how do I get around this?}

  Setting general convergence criteria for multigrid is as much
  art as science. 
  First, it is important to determine if the multigrd solver is
  close to convergence and just dancing around near the desired
  tolerance, but never reaching it, or if it is no where near 
  convergence.  For the latter, it may be that the multigrid
  solver was fed bad data and the problem arose in one of the earlier
  steps.  To get more detail information from the multigrid solver,
  set {\tt mg\_verbose} to a positive integer from 1-4 (the higher
  the number the more information you receive.

  If the multigrid solver is failing during one of the initial
  ``divu'' iterations, it may be because the velocity is initially
  zero, so there is no velocity magnitude to use as a reference for
  convergence, and that ($S - \bar{S}$) is very small (or zero).  In
  this case, it is usually a good idea to perturb the initial state
  slightly, so the righthand side is non-zero.

@@

\item {\em In the final projection in the algorithm, we project
  $U^{n+1}$, using a time-centered $\beta_0$, a time-centered $\rho_0$, but
  an ``$n+1$''-centered $S$.  Why then is the resulting $\phi$ (which then
  defines $\pi$) is at ``$n+1/2$''?}
